Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Re-add some references

There are two main approaches for solving MCS. The first approach (described in \cref{CP}) is based
on CP, whilst the second (described in \cref{clique}) is based on a reformulation of MCS into a
maximum clique problem. Both approaches are described for undirected, unlabelled graphs without
loops; their extension to richer graphs is discussed in \cref{extension}.

@@

In many applications, the common subgraph must be connected. As illustrated in
\cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
during the search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when
combining them. In \cref{mccs-clique}, we introduce a new way for ensuring connectedness in a
clique-based approach. Finally, we compare CP and our clique-based approach in \cref{mccs-eval}.

>>>>

There are two main approaches for solving MCS. The first approach (described in \cref{CP}) is based
on CP, whilst the second (described in \cref{clique}) is based on a reformulation of MCS into a
maximum clique problem. Both approaches are described for undirected, unlabelled graphs without
loops; their extension to richer graphs is discussed in \cref{extension}.  (Other approaches have
been tried, mixed integer programming \cite{DBLP:journals/anor/PivaS12} and heuristics
\cite{DBLP:journals/jcisd/EnglertK15}; SAT encodings seem to struggle even for subgraph isomorphism
\cite{UpcomingIJCAIPaper}.)

@@

In many applications, the common subgraph must be connected
\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
\cite{DBLP:journals/corr/DroschinskyKM16}, but the general case remains \NP-hard. As illustrated in
\cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
during the search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when
combining them. In \cref{mccs-clique}, we introduce a new way for ensuring connectedness in a
clique-based approach. Finally, we compare CP and our clique-based approach in \cref{mccs-eval}.
